---
title: "Warehouse Watts"
subtitle: "Costco deals for cyclists — fuel, hydration, recovery, gear."
format:
  html:
    theme: flatly
    toc: false
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(readr)
library(DT)
library(ggplot2)

read_site <- function(name) {
  path <- file.path("data/site", name)
  if (!file.exists(path)) return(NULL)
  df <- read_csv(path, show_col_types = FALSE)
  if (nrow(df) == 0) NULL else df
}

empty_msg <- function() {
  cat("> Nothing yet — check back Monday.\n\n")
}

fmt_price <- function(x) ifelse(is.na(x), "—", paste0("$", formatC(x, format="f", digits=2)))

make_dt <- function(df, filter = "top", ...) {
  datatable(
    df,
    filter    = filter,
    escape    = FALSE,
    rownames  = FALSE,
    class     = "stripe hover compact",
    options   = list(
      pageLength  = 25,
      dom         = "ftp",
      autoWidth   = TRUE
    ),
    ...
  )
}
```

## 🔥 On Sale Now

```{r on-sale}
df <- read_site("on_sale_now.csv")

if (is.null(df)) {
  empty_msg()
} else {
  df |>
    mutate(
      Item     = ifelse(!is.na(url), paste0('<a href="', url, '" target="_blank">', title, '</a>'), title),
      Price    = price,
      Was      = fmt_price(price_was),
      `% Off`  = ifelse(is.na(pct_off), NA_real_, pct_off),
      Category = category,
      Source   = source
    ) |>
    select(Item, Price, Was, `% Off`, Category, Source) |>
    make_dt() |>
    formatCurrency("Price", digits = 2) |>
    formatStyle("% Off",
      color = styleInterval(0, c("black", "#2e7d32")),
      fontWeight = "bold")
}
```

## 🗣️ Community Buzz

*Prices are community-reported — verify in store before driving out.*

```{r buzz}
df <- read_site("community_buzz.csv")

if (is.null(df)) {
  empty_msg()
} else {
  df |>
    mutate(
      Item     = ifelse(!is.na(url), paste0('<a href="', url, '" target="_blank">', title, '</a>'), title),
      Price    = price,
      Upvotes  = signal,
      Category = category,
      Source   = source,
      Date     = format(as.Date(date), "%b %d")
    ) |>
    select(Item, Price, Upvotes, Category, Source, Date) |>
    make_dt()  |>
    formatCurrency("Price", digits = 2)
}
```

## 🆕 New at Costco

```{r new-items}
df <- read_site("new_items.csv")

if (is.null(df)) {
  empty_msg()
} else {
  df |>
    mutate(
      Item     = ifelse(!is.na(url), paste0('<a href="', url, '" target="_blank">', title, '</a>'), title),
      Price    = price,
      Category = category
    ) |>
    select(Item, Price, Category) |>
    make_dt() |>
    formatCurrency("Price", digits = 2)
}
```

## 📈 Price Trends

```{r trends}
df <- read_site("price_trends.csv")

if (is.null(df) || n_distinct(df$date) < 2) {
  empty_msg()
} else {
  ggplot(df, aes(x = as.Date(date), y = price, color = title, group = title)) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 1.5) +
    facet_wrap(~category, scales = "free_y") +
    scale_x_date(date_labels = "%b %d") +
    scale_y_continuous(labels = scales::dollar) +
    labs(x = NULL, y = NULL, color = NULL) +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      strip.text      = element_text(face = "bold"),
      panel.grid.minor = element_blank()
    )
}
```

## 🏆 Fuel Value Leaderboard

*Lower $/100g carbs = more fuel for your dollar. Electrolyte products (Liquid IV, Zipfizz, coconut water) rank near the bottom — they're not primarily carb sources. Nutrition numbers are from package labels and are approximate; verify before race-day shopping.*

```{r fuel-value}
df <- read_site("fuel_value.csv")

if (is.null(df)) {
  empty_msg()
} else {
  df |>
    mutate(
      Item              = ifelse(!is.na(url), paste0('<a href="', url, '" target="_blank">', title, '</a>'), title),
      Price             = price,
      `$/100g Carbs`    = usd_per_100g_carbs,
      `$/100g Protein`  = usd_per_100g_protein,
      Category          = category
    ) |>
    select(Item, Price, `$/100g Carbs`, `$/100g Protein`, Category) |>
    make_dt() |>
    formatCurrency(c("Price", "$/100g Carbs", "$/100g Protein"), digits = 2)
}
```

---

::: {.text-muted style="font-size:0.85em; text-align:center;"}
Not affiliated with Costco. Hobby project. Data may be wrong. Last updated `r format(Sys.Date(), "%B %d, %Y")`.
If a link doesn't work, search for the product directly at [costco.com](https://www.costco.com).
:::
